\TitleFont Compressively sampled speech: How good is the recovery?

### 2020-08-16 Response to Reviewer Comments.tex

		By ``At face value'', we are referring to the value of PESQ. To avoid confusion, we have replaced the sentence to the following:

		\begin{quotation}
			\textcolor{Green}{By inspection of the PESQ value alone, we can tell that the reconstructed signal quality is slightly below average.}
		\end{quotation}

		\item \textbf{How do you determine ``slightly below average''?}

		The PESQ algorithm was modeled on subjective scoring systems. Such systems would ask people to rate an output signal, say, an integer from 1 to 5, given the input signal. In that case, 1 would correspond to bad, and 5 excellent. The output of PESQ is a float, but the authors still have opted to label the integer scores as 1.0 - bad, 2.0 - below average, 3.0 - average, 4.0 - good, 5.0 - perfect. The test signal yielded a PESQ value of 2.50, which is slightly below average.
	\end{enumerate}

	\item
		\begin{enumerate}
			\item \textbf{Please incorporate changes that you mentioned in your reply to the reviewer but was not added to the manuscript. For example, add the conversion table from number to qualitative description -- "slightly below average".}

			We have added Table 1 in Sec.~2.4 for the conversion of PESQ from quantitative to qualitative. In the preceding paragraph, the following sentence has been added:

			\begin{quotation}
				...models the obsolete mean opinion scores (MOS). \textcolor{Green}{Its output is a float in the range $[1, 5]$ with corresponding qualitative descriptions at integer values, as shown in Table~1.}
			\end{quotation}
		\end{enumerate}
\end{enumerate}

### 2020-08-16 main.tex
2nd reviewer revisions

\documentclass[10pt,a4paper,twoside]{article}
\input{spp}
\usepackage{physics}
\usepackage{amsfonts}
\usepackage{changes}
\usepackage{graphicx}
\graphicspath{{images/}}
\newcommand{\snrseg}{SNR$_{\mathrm{seg}}$}

@@

\subsection{Reconstruction evaluation}\label{ssec:eval}
Reconstruction quality was evaluated using PESQ, which is a full-reference, perceptually intuitive scoring system which models the obsolete mean opinion scores (MOS). Due to the complexity of the algorithm, we refer the reader to Sec.~10 of the PESQ manual \cite{pesq} for an in-depth discussion.

The \snrseg~, defined as

>>>>

\documentclass[10pt,a4paper,twoside]{article}
\input{spp}
\usepackage{physics}
\usepackage{amsfonts}
\usepackage{tabularx}
\usepackage{graphicx}
\graphicspath{{images/}}
\newcommand{\snrseg}{SNR$_{\mathrm{seg}}$}

@@

\subsection{Reconstruction evaluation}\label{ssec:eval}
Reconstruction quality was evaluated using PESQ, which is a full-reference, perceptually intuitive scoring system which models the obsolete mean opinion scores (MOS). Its output is a float in the range $[1, 5]$ with corresponding qualitative descriptions at integer values, as shown in Table~\ref{tab:pesq}. Due to the complexity of the algorithm, we refer the reader to Sec.~10 of the PESQ manual \cite{pesq} for an in-depth discussion.

\begin{table}[htb]
	\centering
	\caption{PESQ integer values and their corresponding qualitative descriptions.}
	\label{tab:pesq}
	\begin{tabularx}{\textwidth}{ >{\bfseries}r *{5}{| >{\centering\arraybackslash}X} }
		PESQ value & 1 & 2 & 3 & 4 & 5 \\
		Description & bad & below average & average & good & perfect
	\end{tabularx}
\end{table}

The \snrseg, defined as
